\begin{enumerate}
    \item \texttt{matrixTest}
    \begin{itemize}
        \item Use the \texttt{listings} package to include your \texttt{matrixTest} output in the pdf.
        \item For each bug, use the \texttt{listings} package to display the original line of code with the error, as well as the fix.  Describe the error.            
    \end{itemize}
    \textbf{ANSWER:} \lstinputlisting[language={}]{gdbOutput.txt}
    The for loop has an equals sign as a parameter but there shouldn't be one because it's accessing unallocated areas of an array.

    \item \texttt{fibonacci}
    \begin{itemize}
        \item Use the \texttt{listings} package to include your \texttt{fibonacci} output in the pdf.
        \item For each bug, use the \texttt{listings} package to display the original line of code with the error, as well as the fix.  Describe the error.
    \end{itemize}
    \textbf{ANSWER:} \lstinputlisting[language={}]{fibOutput.txt}
    The memory wasn't allocated right, we forgot to multiply by the size of an int when instantiating the array.

    \item \texttt{pascal}
    \begin{itemize}
        \item Use the \texttt{listings} package to include your \texttt{pascal} output in the pdf.
        \item For each bug, use the \texttt{listings} package to display the original line of code with the error, as well as the fix.  Describe the error.
    \end{itemize}
    \textbf{ANSWER:} \lstinputlisting[language={}]{pasOutput.txt}
    Something is wrong with the calculations and spacing, commented out the right spacing because it wasn't right.

    \item \texttt{array\_sum}
    \begin{itemize}
        \item Use the \texttt{listings} package to include your \texttt{array\_sum} output in the pdf.
        \item For each bug, use the \texttt{listings} package to display the original line of code with the error, as well as the fix.  Describe the error.
    \end{itemize}
    \textbf{ANSWER:} \lstinputlisting[language={}]{sumOutput.txt}
    No bugs found.

    \item \texttt{rotate\_vector}
    \begin{itemize}
        \item Use the \texttt{listings} package to include your \texttt{rotate\_vector} output in the pdf.
        \item For each bug, use the \texttt{listings} package to display the original line of code with the error, as well as the fix.  Describe the error.
    \end{itemize}
    \textbf{ANSWER:} \lstinputlisting[language={}]{rotOutput.txt}
    When filling the rows of array with vector rotations, the nested for loop incremented i instead of j, so I changed it from i++ to j++.
    
\end{enumerate}
